Baseline centering problem

### 2018-12-17 paper/tangotd.tex

Here we do not have access to $\Delta$, but have access to transitions
$s\to s'$, which are samples of
$\rho\Delta$, namely, $\rho\Delta=\E_{s,s'} 1_s\transp{(\1_s-\gamma
\1_{s'})}$. This corresponds to a stochastic version of the Newton
method, with learning rate $\eta\ll 1$,
\begin{equation}
A\gets A+\eta A-\eta A 1_s\transp{(\1_s-\gamma \1_{s'})} A
\end{equation}
Indeed, in expectation over $s\to s'$ this corresponds to $A\gets A+\eta
A-\eta A \rho\Delta A$, which converges to $A=\Delta^{-1}\rho^{-1}$. This
also corresponds to the rank-one update formyla for matrix inversion,
$(D+\eta u\transp{v})^{-1}=D^{-1}-\eta
D^{-1}u\transp{v}D^{-1}+O(\eta^2)$. Namely,
if we update our estimate of $\rho\Delta$ by
$\rho\Delta\gets (1-\eta)\rho\Delta+\eta 1_s\transp{(\1_s-\gamma
\1_{s'})}$ when a transition $s\to s'$ is observed, then
$(\rho\Delta)^{-1}$ gets updated as above.

With $A=\green\cdot \E_{\rho} f$ as above, everything is fully samplable.
It is not clear to me how to mix the left, right and middle Bellman
equations, but the correspondence with path combinatorics and the Newton
method suggests this
might be an important point for the navigation problem.

>>>>

Here we do not have access to $\Delta$, but have access to transitions
$s\to s'$, which are samples of
$\Delta$, namely, $\Delta=\sum_s\E_{s'\sim P(s'|s)} \1_s\transp{(\1_s-\gamma
\1_{s'})}$. This corresponds to a stochastic version of the Newton
method, with learning rate $\eta\ll 1$,
\begin{equation}
A\gets A+\eta A-\eta A \E_{ss'} \frac{1}{\rho(s)}\1_s\transp{(\1_s-\gamma \1_{s'})} A
\end{equation}
Indeed, in expectation over $s\to s'$ this corresponds to $A\gets A+\eta
A-\eta A \Delta A$, which converges to $A=\Delta^{-1}$. This
also corresponds to the rank-one update formyla for matrix inversion,
$(D+\eta u\transp{v})^{-1}=D^{-1}-\eta
D^{-1}u\transp{v}D^{-1}+O(\eta^2)$. Namely,
if we update our estimate of $\Delta$ by
$\Delta\gets (1-\eta)\Delta+\eta \frac{1}{\rho(s)} \1_s\transp{(\1_s-\gamma
\1_{s'})}$ when a transition $s\to s'$ is observed, then
$\Delta^{-1}$ gets updated as above.

With $A=\green\cdot \E_{\rho} f$ as above, everything is fully samplable
(thanks to the $\E_\rho$ which cancels the $1/\rho$ factors), see below.
It is not clear to me how to mix the left, right and middle Bellman
equations, but the correspondence with path combinatorics and the Newton
method suggests this
might be an important point for the navigation problem.

Namely, set
\begin{equation}
A=\transp{\green}F, \qquad \green=\sum_s \green(s)\1_s,\qquad F=\E_{s\sim
\rho}
f(s)\1_s
\end{equation}
which is the same representation as above, namely $A=\Delta^{-1}$ is
equivalent to $\transp{\1_s}\green(s)\cdot \E_{s'\sim
\rho} \psi(s')f(s')=\transp{\1_s}\Delta^{-1}\psi$ for all $s$ and test
functions $\psi$.
